How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-06-14 Draft_June_2022/Full_draft_20220608.rmd
Updated plot labs to make them more intuitive

       y = "Share of environmental conservation",
       title = "Amazon constructions as an issue of environmental conservation\nin relation to distance from the Amazon",
       subtitle = "Distance as a straight line from state, or country, capital from the Amazon in kilometers",

>>>>

       y = "The Amazon as an issue of environmental conservation",
       title = "Amazon constructions as an issue of pure environmental conservation\nin relation to distance from Manaus",
       subtitle = "Distance as a straight line from state or country's capital to Manaus in kilometers",
